Vv caluclator

### 2023-02-09 code/analysis_code/exploratory_vp.qmd
Corrections to Vv and Vp calcs

Data
```{r}
vp<- read_csv(file = here("data", "processed_data", "vp_clean_copies_date.csv")) #This file had dates manually added
sq <-read_csv(here("data", "raw_data", "vp_qPCR_0.csv")) #Manually replaced NaN with 0 for no amplifcation 
```
Standard Curve
```{r}
std<- sq %>%
  filter(
    Fluor %in% "HEX",
    Content %in% "Std")

@@

rd_vp
```

Save Vp C2/RD as PNG
```{r}
png(file = here("results", "plots", "vp_c2.png")) #Saving c2
c2_vp
dev.off()

png(file = here("results", "plots","vp_rd6.png")) #Saving RD
rd_vp
dev.off()
```

>>>>

Data
```{r}
vp<- read_csv(file = here("data", "processed_data", "vp_clean_copies_date.csv")) #This file had dates manually added
sq <-read_csv(here("data", "raw_data", "vp_qPCR.csv")) #Manually replaced NaN with 0 for no amplifcation 
```
Standard Curve
```{r}
std<- sq %>%
  filter(
    Fluor %in% "HEX",
    Content %in% "Std")

@@

rd_vp
```
All Sites
```{r}
all<- vp %>% 
    mutate(site = recode(site, "BO" = "Blind Oso",
                              "C2" = "Canals",
                              "RD" = "Gulf")) %>%
  ggplot() + geom_line(
  aes(x = date,
      y = copies_mL,
      color = site)) +
  facet_wrap(~site)+
  geom_point(
    aes(x = date,
      y = copies_mL,
      color = site))+
  theme_bw() +
  labs(x = "Date",
       y = "Copies/mL",
       title = "Vp at All Sites") +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5)) +

 scale_color_manual( values = c("Blind Oso" = "darkgreen",
                                "Canals" = "darkred",
                                "Gulf" = "darkblue"))

all
```

Save Vp C2/RD as PNG
```{r}
png(file = here("results", "plots", "vp_all_sites.png")) #Saving c2
all
dev.off()

### 2023-02-09 code/analysis_code/exploratory_vv.qmd
Corrections to Vv and Vp calcs

Data
```{r}
vv<- read_csv(file = here("data", "processed_data", "vv_clean_copies_date.csv")) #This file had dates manually added
sq <-read_csv(here("data", "raw_data", "vv_qPCR_daily_0.csv"))
```

Vv Standard Curve
```{r}
std<- sq %>%
  filter(Content %in% "Std",
         Fluor %in% "HEX") #%>%
  #ggplot() + geom_point(
  #  aes(x = log(SQ),
      #  y = Cq))
#std
```

@@

All sites
```{r}
all<- vv %>% 
  mutate(site = recode(site, "BO" = "Blind Oso",
                              "C2" = "Canals",
                              "RD" = "Gulf")) %>%
  ggplot() + geom_line(
    aes(x = date,
        y = copies_mL,
        color = site)) + 
  scale_color_manual( values = c("Blind Oso" = "darkgreen",
                                "Canals" = "darkred",
                                "Gulf" = "darkblue"))+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date", 
    y = "Copies/mL",
    title = "Vibrio vulnificus Levels Across Dust Time Series")+
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5))

all
```

@@

>>>>

Data
```{r}
vv<- read_csv(file = here("data", "processed_data", "vv_clean_copies_date.csv")) #This file had dates manually added
#sq <-read_csv(here("data", "raw_data", "vv_qPCR_daily_0.csv"))
redo<- read_csv(here("data", "processed_data", "vv_clean_copies_redo_date.csv"))
```

Vv Standard Curve
```{r}
#std<- sq %>%
 # filter(Content %in% "Std",
        # Fluor %in% "HEX") #%>%
  #ggplot() + geom_point(
  #  aes(x = log(SQ),
      #  y = Cq))
#std
```

@@

All sites
```{r}
all<- vv %>% 
  mutate(site = recode(site, "BO" = "Blind Oso",
                              "C2" = "Canals",
                              "RD" = "Gulf")) %>%
  ggplot() + geom_line(
    aes(x = date,
        y = copies_mL,
        color = site)) + 
  scale_color_manual( values = c("Blind Oso" = "darkgreen",
                                "Canals" = "darkred",
                                "Gulf" = "darkblue"))+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date", 
    y = "Copies/mL",
    title = "Vibrio vulnificus Levels Across Dust Time Series: Trial 1")+
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5))

all
```
All Redo
```{r}
all_redo<- redo %>% 
  mutate(site = recode(site, "BO" = "Blind Oso",
                              "C2" = "Canals",
                              "RD" = "Gulf")) %>%
  ggplot() + geom_line(
    aes(x = date,
        y = copies_mL,
        color = site)) + 
  scale_color_manual( values = c("Blind Oso" = "darkgreen",
                                "Canals" = "darkred",
                                "Gulf" = "darkblue"))+
  theme_bw()+
  facet_wrap(~site)+
  labs(
    x = "Date", 
    y = "Copies/mL",
    title = "Vibrio vulnificus Levels Across Dust Time Series: Trial 2")+
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(hjust = 0.5))

all_redo
```

@@

png(file = here("results", "plots", "vv_all_sites_redo.png")) #Saving c2
all_redo
dev.off()

### 2023-02-09 code/processing_code/vp_copies_calculator.qmd
Corrections to Vv and Vp calcs

Load data
```{r}
sq <-read_csv(here("data", "raw_data", "vp_qPCR_0.csv")) #Manually replaced NaN with 0 for no amplifcation 
```
Filter for HEX dye (samples). Cy5 is for IAC
```{r}
sq2<- sq %>% 
  select(filter_amt,SQ, Sample, Fluor) %>%
  filter(Fluor %in% "HEX")

@@

Drop NAs
```{r}
copies3<- copies2 %>% filter(!is.na(copies_mL)) %>% #Dropping NAs from STD Curve
  select(copies_mL,site, Sample)
```
*Dropping NAs got rid of BO completely*

>>>>

Load data
```{r}
sq <-read_csv(here("data", "raw_data", "vp_qPCR.csv")) 
```
Filter for HEX dye (samples). Cy5 is for IAC
```{r}
sq2<- sq %>% 
  select(filter_amt,SQ, Sample, Fluor) %>%
  filter(Fluor %in% "HEX")

@@

Change NA to 0 and drop STD CRV NAs
```{r}
copies3<- copies2 %>% 
 mutate(copies_mL = ifelse(is.na(copies_mL), 0, copies_mL)) %>%
filter(!is.na(Sample))  #Dropping NAs from STD Curve
```
*Dropping NAs got rid of BO completely*

### 2023-02-09 code/processing_code/vv_copies_calclulator.qmd
Corrections to Vv and Vp calcs

Load data
```{r}
sq <-read_csv(here("data", "raw_data", "vv_qPCR_daily_0.csv")) #Manually replaced NaN with 0 for no amplifcation, added filter_amt and dilution
redo<- read_csv(here("data", "raw_data", "vv_qPCR_daily_0_redo.csv")) #Manually replaced NaN with 0 for no amplifcation, added filter_amt and dilution
```

@@

redo2<- redo %>% 
  select(filter_amt,Cq, Sample, Fluor, dilution) %>%
  filter(Fluor %in% "HEX")

@@

SQ --> Copies/mL
```{r}
copies<- sq2 %>%
    mutate(
    log_sq = ((Cq-34.934)/-3.1444), #Equation of the line to get log(SQ)
    sq = 10^log_sq, #Unlog 
    copies_rxn = sq*15, #SQ*Reaction Volume
    copies_uL_1_10 = copies_rxn/1.2, #Copies/RXN / DNA Template Volume
    copies_uL_extract = copies_uL_1_10 *dilution, #(Copies/uL of 1:10)*(1 if there was no sample dilution // *10 if there was a 1:10 dilution etc.)
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL_extract*concentration_factor)%>%

@@

copies_redo<- redo2 %>%
    mutate(
    log_sq = ((Cq-34.934)/-3.1444), #Equation of the line to get log(SQ)
    sq = 10^log_sq, #Unlog 
    copies_rxn = sq*15, #SQ*Reaction Volume
    copies_uL_1_10 = copies_rxn/1.2, #Copies/RXN / DNA Template Volume
    copies_uL_extract = copies_uL_1_10 *dilution, #(Copies/uL of 1:10)*(1 if there was no sample dilution // *10 if there was a 1:10 dilution etc.)
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL_extract*concentration_factor)%>%

@@

Drop NAs
```{r}
copies3<- copies2 %>% 
  filter(!is.na(copies_mL)) %>% #Dropping NAs from STD Curve
  select(copies_mL,site, Sample)

copies3_redo<- copies2_redo %>%
   filter(!is.na(copies_mL)) %>% #Dropping NAs from STD Curve
  select(copies_mL,site, Sample)
```

>>>>

Load data
```{r}
sq <-read_csv(here("data", "raw_data", "vv_run_daily_TX_dust_2_7_23 -  Quantification Summary.csv")) #Manually replaced NaN with 0 for no amplifcation, added filter_amt and dilution
redo<- read_csv(here("data", "raw_data", "vv_run_daily_TX_dust_2_9_23 -  Quantification Summary.csv")) #Manually replaced NaN with 0 for no amplifcation, added filter_amt and dilution
```

@@

redo2<- redo %>% 
  select(filter_amt,Cq, Sample, Fluor, dilution, Well) %>%
  filter(Fluor %in% "HEX",
         !Well %in% "K19")

SQ_test<- sq %>% 
  select(filter_amt,SQ,Cq, Sample, Fluor, dilution) %>%
  filter(Fluor %in% "HEX")

@@

Cq --> Copies/mL
```{r}
copies<- sq2 %>%
   mutate(
   log_sq = ((Cq-36.497)/-3.166), #Equation of the line to get log(SQ)
    sq = 10^log_sq, #Unlog 
    copies_rxn = sq*15, #SQ*Reaction Volume
    copies_uL_1_10 = copies_rxn/1.2, #Copies/RXN / DNA Template Volume
    copies_uL_extract = copies_uL_1_10 *dilution, #(Copies/uL of 1:10)*(1 if there was no sample dilution // *10 if there was a 1:10 dilution etc.)
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL_extract*concentration_factor) %>%

@@

copies_redo<- redo2 %>%
    mutate(
    log_sq = ((Cq-36.497)/-3.166), #Equation of the line to get log(SQ)
    sq = 10^log_sq, #Unlog 
    copies_rxn = sq*15, #SQ*Reaction Volume
    copies_uL_1_10 = copies_rxn/1.2, #Copies/RXN / DNA Template Volume
    copies_uL_extract = copies_uL_1_10 *dilution, #(Copies/uL of 1:10)*(1 if there was no sample dilution // *10 if there was a 1:10 dilution etc.)
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL_extract*concentration_factor) %>%

SQ_test1<- sq %>%
    mutate(
   # log_sq = ((Cq-36.497)/-3.166), #Equation of the line to get log(SQ)
   # sq = 10^log_sq, #Unlog 
    copies_rxn = SQ*15, #SQ*Reaction Volume
    copies_uL_1_10 = copies_rxn/1.2, #Copies/RXN / DNA Template Volume
    copies_uL_extract = copies_uL_1_10 *dilution, #(Copies/uL of 1:10)*(1 if there was no sample dilution // *10 if there was a 1:10 dilution etc.)
    concentration_factor = 100/filter_amt, #(Concentration factor = amount of eluted DNA from ZYMO) / (filter amount from vacuum filtration)
    copies_mL = copies_uL_extract*concentration_factor) %>%

@@

Replace NaN with 0 for copies/mL
```{r}
copies3<- copies2 %>% 
 mutate(copies_mL = ifelse(is.na(copies_mL), 0, copies_mL)) %>%
filter(!is.na(Sample))  #Dropping NAs from STD Curve

copies3_redo<- copies2_redo %>%
 mutate(copies_mL = ifelse(is.na(copies_mL), 0, copies_mL)) %>%
filter(!is.na(Sample))  #Dropping NAs from STD Curve
```
